
---
title:  Closing statistics condition|
     

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:
  m: NA
  n: NA
  s: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```



# Introduction
According to the SEEA (System of Environmental-Economic Accounting) Ecosystem Accounting, this report generates ecosystem condition account records. These records display the minimum, mean, maximum, and standard deviation (SD) of the statistical values of the condition indicators across the region. All the condition indicators are harmonized together, and the popups displayed on the map provide more detailed information about the condition indicators. Additionally, the report includes metadata information.

## Ecosystem Condition  map
Figure 1 below shows the ecosystem condition indicatores map of the region


```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

# All defaults

   
   mapview(params$m)



 
```
*Figure 1: Shows the  Map of Total  Geography Extent of the  Habitat in Opening Year* 

## SEEA Condtion Accounting Table

Below, we can see the table which shows the condition statistics Min,Mean,Max,SD.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults
datatable(

   
   data.frame(  params$n
) 
)



 
```
*Figure 2: Shows the  Map of Total  Geography Extent of the  Habitat in Opening Year* 


### Meta data


```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults
datatable(

   
   data.frame(  params$s
) 
)



 
```
*Figure 2: Shows the  Map of Total  Geography Extent of the  Habitat in Opening Year* 
