
---
title:  SEEA Condition Change Accounting Report|

     

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:
  n: NA
  s: NA
  o: NA
  m: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```

# Introduction
In this section, we will analyze the changes in the overall condition of the total area. We will explore the minimum, mean, maximum, and standard deviation, as well as the net change in condition. Additionally, we will compare these measurements with the reference and targeted elements to monitor the variation in condition change within the region.


# Habitat Condition Change Maps
The ecosystem condition accounting map enables monitoring and assessment of every location's health. By classifying and symbolizing areas based on condition, it helps identify areas in good health or degradation.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}
   mapview(params$m, maxpixels = 900000000)



```
*Figure 1: This map shows the total ecosystem condition area between two correctional intervals* 


## Total Condition Change Statistics
The overall condition accounting change table provides information about the condition of the entire geographical area. The minimum value represents the lowest observed condition, the maximum value represents the highest observed condition, and the mean value represents the average condition across the area. The standard deviation indicates the degree of variation or spread in the condition values. We can also measure the net change in the condition of two consecutive intervals.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults
datatable(
   as.data.frame(  params$n
) 
)
```
*Table 1: Overall Condition Accounting Change Table* 

## Meta data

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults
datatable(
   data.frame(  params$s
) 
)
```
