
---
title: Habitat transformation markers map report|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny  
params:

  n: NA
  d: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---



# Introduction
In this report, we present the habitat transformation map and the metadata information. The map shows how a specific habitat is being transformed from one class to another, indicating locations with high and low levels of transformation. Each marker provides detailed information about the habitat, such as its latitude, longitude, and transformation data.

```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}


params$n


```
*Figure 1: Habitat transformation markers map.*

# Meta data


```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}

datatable(data.frame(params$d),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```