
---
title:  Habitat Extent and Condition Accounting Closing|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny  
params:

  n: NA
  m: NA
  d: NA
  q: NA
  w: NA
  e: NA
  z: NA
  x: NA
  c: NA
  v: NA
  s: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---



# Introduction
Worldwide, ecosystem services are impacted by disturbances that operate at various scales and intensities. However, due to an increase in coastal development and global climate change impacts, disturbances on ecosystem are now occurring at increasing frequencies and intensities. Therefore, long-term ecological monitoring programs are essential to follow ecosystem change and subsequent recovery after disturbances, and are often set up to inform stakeholders on ecosystem status.

## Markers of Habitat Transformation 

The below figure Shows The habitat transformation Markers  Maps

```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}

params$n

```


## Ecosystem Extent Asset Account {.tabset .tabset-fade}
### Habitat Opening statistics 
```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}



datatable(params$m, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```



```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}

params$q

```



```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}

params$w

```



## Condition Closing Stocks {.tabset .tabset-fade}


```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}
mapview(
params$s)

```
## Condition Total Geographical Extent {.tabset .tabset-fade}


```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}


datatable(params$e, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```



## Ecosystem Extent Asset Account {.tabset .tabset-fade}
### Habitat Condition Min  
```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}



datatable(params$z, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```
### Habitat Condition Mean  
```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}



datatable(params$x, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```
### Habitat Condition Max  
```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}



datatable(params$c, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```

### Habitat Condition SD  
```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}



datatable(params$v, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```


## Metadata  {.tabset .tabset-fade}


```{r echo=FALSE, message=FALSE,warning=FALSE, paged.print=FALSE}




datatable(params$d, options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```



