
---
title: SEEA habitat change extent accounting report |

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  o: NA
  m: NA
  q: NA
  n: NA
  s: NA
  w: NA
  e: NA
  z: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```



# Introduction
This report generates the SEEA (System of Environmental-Economic Accounting) ecosystem extent account, which shows the total area of each ecosystem type within a specified area, the percentage of habitats, and any changes over time. The report includes several accounting tables, such as the ecosystem extent asset account, SEEA change matrix, and percentage of habitat change table. Additionally, to provide a better visualization of the data, the report generates several habitats change graphs and maps. Finally, the report also provides metadata information. 

## Ecosystem extent Map

The figure below depicts how habitats have changed over two time periods: opening and closing presides. Here, we can observe the changes in habits during two different intervals.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults


                params$o



 
```
*Figure 1: This map shows the total ecosystem extent area between two correctional intervals* 

## SEEA Extent Accounting Tables {.tabset .tabset-fade}
Below, we can see the SEEA change matrix, habitat Percentage change table, and ecosystem extent asset account table. The SEEA change matrix provides insight into the transformation of habitats during two-time intervals. The table on habitat change in area and percentages illustrates how habitat areas have changed and their corresponding percentages. Additionally, the ecosystem extent asset account provides detailed information on the additions, subtractions,and Net change of habitats. 

### SEEA change matrix 


```{r echo=FALSE, message=TRUE, paged.print=FALSE}
# All defaults
datatable(params$m,options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```


*Table 1: SEEA habitat change matrix.* 

### Habitat Percentage Change  

```{r echo=FALSE, message=TRUE, paged.print=FALSE,}
datatable(params$q,options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

    

```
*Table-2: changes in habitat area and percentages change * 

### Ecosystem Extent Asset Account 

```{r echo=FALSE, message=TRUE, paged.print=FALSE,}

datatable(params$n,options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```
*Table-3: Ecosystem Extent Asset Account* 


## Habitat Percentage Change Graph{.tabset .tabset-fade}

The graph presents detailed information on how the percentage of habitat areas has been changing over two cross-section intervals. The x-axis indicates the habitat classes, while the y-axis represents the percentage values.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,}

params$w
```

*Figure 2: Showed The Habitat Percentage Change graph* 



## Habitat Area Change Graph{.tabset .tabset-fade}

The graph presents detailed information on how the Area of habitat areas has been changing over two cross-section intervals. The x-axis indicates the habitat classes, while the y-axis represents the Area values.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,}

params$z
```

*Figure 3: Showed The Habitat Area Change graph* 



## Habiter difference in percentage Graph{.tabset .tabset-fade}

The graph presents detailed information on how the difference in the percentage of habitats is changing between two time periods.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,}

params$e
```

*Figure 4: Showed The habituate difference in percentage graph*




### Metadata  

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(params$s,options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```
