
---
title:  SEEA Condition Accounting Report|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:
  q: NA
  m: NA
  n: NA
  s: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(mapview)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```



# Introduction
According to the SEEA (System of Environmental-Economic Accounting) Ecosystem Accounting, this report generates ecosystem condition account records. These records display the minimum, mean, maximum, and standard deviation (SD) of the statistical values of the condition indicators across the region. All the condition indicators are harmonized together, and the popups displayed on the map provide more detailed information about the condition indicators. Additionally, the report includes metadata information.

## Ecosystem Condition  map
The ecosystem condition accounting map enables monitoring and assessment of every location's health. By classifying and symbolizing areas based on condition, it helps identify areas in good health or degradation.


```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

# All defaults

   
   mapview(params$m)

```
*Figure 1: Shows the condition indicators map.* 

## SEEA Condtion Accounting Table

The overall SEEA condition accounting table provides information about the condition of the entire geographical area. The minimum value represents the lowest observed condition, the maximum value represents the highest observed condition, and the mean value represents the average condition across the area. The standard deviation indicates the degree of variation or spread in the condition values.

```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

# All defaults

   

datatable(round(data.frame(params$n),2),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

```
*Table 1: Shows the condition statistics * 

### Meta data

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$s),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```


