
---
title:  SEEA Opening Condition Accounting Statistics Report|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:
  m: NA

  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(mapview)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```


# Introduction
According to the SEEA (System of Environmental-Economic Accounting) Ecosystem Accounting, this report generates ecosystem condition account records. 
These records display the minimum, mean, maximum, and standard deviation (SD) of the statistical values of the condition indicators across the region. 
All the condition indicators are harmonized together, and the popups displayed on the map provide more detailed information about the condition indicators. Additionally, the report includes metadata information.

## Ecosystem Condition map
Figure 1 below shows the ecosystem condition indicators map of the region


```{r echo=FALSE, message=TRUE, paged.print=FALSE,warning=FALSE}

# All defaults

   
   mapview(params$m)

```
*Figure 1: Shows the condition indicators map.* 
