
---
title:  Habitat Extent and Condition Accounting|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  n: NA

  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```



# Introduction
Worldwide, ecosystem services are impacted by disturbances that operate at various scales and intensities. However, due to an increase in coastal development and global climate change impacts, disturbances on ecosystem are now occurring at increasing frequencies and intensities. Therefore, long-term ecological monitoring programs are essential to follow ecosystem change and subsequent recovery after disturbances, and are often set up to inform stakeholders on ecosystem status.

## Key Geography Regions

The below map highlights the total extent of ecosystem  extent ecosystem services come from these ecosystems. The map helps to understand how 
the extent of the ecosystem services are distributed in different locations. 

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults


                params$n



 
```
    
    
*Figure 1: Shows the  Map of the  Geography Extent* 

