
---
title: SEEA habitat extent accounting report|

output: 
 html_document:
   theme: flatly # default, cerulean, journal, flatly, darkly, readable, spacelab, united, cosmo, lumen, paper, sandstone, simplex, and yeti
   highlight: tango # default, tango, pygments, kate, monochrome, espresso, zenburn, haddock, breezedark, and textmate
   smart: true
   toc: true
   toc_depth: 2
   toc_float:
     collapsed: false
     smooth_scroll: false
   numbers_sections: true
   fig_width: 7
   fig_height: 6
   fig_caption: true
   df_print: paged

runtime: shiny   
params:

  n: NA
  m: NA
  o: NA
  p: NA
  q: NA
  s: NA
  minimum: 
    label: "Minimum:"
    value: 100
    input: slider
    min: 0
    max: 1000
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(1234)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)
library(purrr)

```
# Introduction 

As per the SEEA (System of Environmental-Economic Accounting) ecosystem Accounting, this report generates ecosystem extent accounts record, which shows the total area of each ecosystem, classified by type within a specified area.  Additionally, to provide a better visualization of the data, the report generates several habitat graphs and maps. Finally, the report also provides metadata information. 


## Ecosystem extent Map

The displayed map depicts the extent of the ecosystem, presenting a visual representation of the entire geographic area it encompasses. It provides valuable insight into the overall size and boundaries of the region, allowing for a better understanding of the ecosystem's spatial extent and connectivity.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults


                params$m



 
```

*Figure 1: Total ecosystem extent area map.* 

## SEEA Extent Accounting Table

Presented below is a table illustrating the habitat classes alongside the habitat area stated in hectares and the corresponding habitat percentage. This table offers a clear overview of the sizes and proportions of different habitats, enabling a deeper understanding of their distribution and ecological significance within the given region.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

datatable(data.frame(params$o),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))

    

```

*Table 1: Habitat area and percentage table.*


Displayed below is a bar graph depicting the variation in habitat areas measured in hectares. This visual representation provides a clearer understanding of the disparities in habitat sizes within the region. The graph enables easy comparison and highlights the relative dominance or scarcity of specific habitats based on their respective areas

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

params$q


```
*Figure 2: Habitat area in hectares.* 

The bar graph presented below showcases the variability in habitat percentages within a given region. This graphical representation offers a visual comparison of the proportional distribution of different habitats, allowing for a better understanding of the relative abundance or scarcity of each habitat class. It aids in identifying significant variations in habitat composition and concentration

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

# All defaults

params$p


```
*Figure 3: Habitat percentage.* 





### Meta data  

Below, we can find the metadata information, which provides detailed insights and descriptions about the data set you are referring to.

```{r echo=FALSE, message=TRUE, paged.print=FALSE}

datatable(data.frame(params$s),options = list(
  dom = 't',
  scrollX = TRUE,
  scrollCollapse = TRUE
))


```

